XOr-Some Bayesian Power analysis

### 2021-10-05 analysis/power/xor-some_bayesian-power.Rmd
simplified minimal Bayesian power script

>>>>

# MF's crowbar ignoramus approach

```{r, eval = FALSE}
# create fake data
create_fake_data <- function(N = 100, seed = 1) {
  set.seed(seed)
  beta_rel  <- 0.15
  beta_comp <- 0.15
  beta_pri  <- 0.15
  map_df(
    1:N, 
    function(i) {
      tibble(
        subj    = rep(str_c("subj_",i), times = 4),
        rel     = rnorm(4),
        comp    = rnorm(4),
        pri     = rnorm(4)
      ) %>% 
        group_by(subj) %>% 
        mutate(
          rel     = (rel-mean(rel)) / sd(rel),
          comp    = (comp-mean(comp)) / sd(comp),
          pri     = (pri-mean(pri)) / sd(pri)
        ) %>% 
        ungroup() %>% 
        mutate(
          target  = rnorm(4, beta_rel * rel + beta_comp * comp + beta_pri * pri)
        )
    }
  )
}
initial_fake_data <- create_fake_data(N=100, seed = 1234)

# initial fit
fit_initial <- brm(target ~ rel * comp * pri, initial_fake_data)

# main results
N <- 300
k <-10

results <- map_dbl(
  1:k, 
  function(i) {
    fake_data <- create_fake_data(N=N, seed = i)
    fit <- update(fit_initial, newdata = fake_data, seed = i, cores = 4)
    lower_bounds <- rbind(
      aida::summarize_sample_vector(brms::posterior_samples(fit)[,'b_rel'], "rel"),
      aida::summarize_sample_vector(brms::posterior_samples(fit)[,'b_comp'], "comp"),
      aida::summarize_sample_vector(brms::posterior_samples(fit)[,'b_pri'], "pri")
    ) %>% pull("|95%")
    min(lower_bounds)
  }
)

message("Effective power for N=", N, " is:" , mean(results > 0.05))
```
